### 2016-03-08 paper/algorithm.tex
yasu

Our framework is general, and it is easy to verify that existing
parallel fusion algorithms are just our special cases.
%
For example, the parallel fusion algorithm by Lempitsky et
al.~\cite{viktor} always performs binary fusion between the current
solution and another label, which can be achieved by setting $\alpha_i =
1$ and $\beta_i = 0$ for all the threads. The algorithm by
Veksler~\cite{olga} or Dejong et al.~\cite{dejong} hierarchically fuses
solutions starting from solution proposals. The algorithm can be
realized by setting $\alpha_i = 1, \beta_i = 0$ initially, then use
$\alpha_i = 0, \beta_i=1$  for the rest of the algorithm.

standard models.

We now illustrate the power of Swarm Fusion framework for three problems
in Computer Vision.

Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
configuration, the first thread $T_1$ fuses its current solution $S_1$,
two new proposal solutions (e.g., by randomly picking two proposal
generation schemes), and the current solutions $(S_2, S_3, S_4)$ in the
other three threads. This is a multi-way fusion with a non-submodular
energy in general, and message passing algorithm such as
TRW~\cite{kolmogorov} can be used. Sequential QPBO application is
another.

Our model is flexible. For example, a parallel fusion move algorithm by
Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_i$

, and it is easy to see that 
Existing parallel fusion techniques are special

Our model is flexible and

>>>>

\mysubsubsection{Base architecture}
The swarm fusion is highly flexible, and we first introduce our base
architecture that exploits general strenghts offered by the
framework. Later, we explain how to further optimize the configuration
to boost performance for specific problems. In the base architecture,
all the threads fuse some number of proposals from the proposal pool and
some number of solutions from the solution pool in each step. In other
words, all the threads constantly exchange solutions while injecting new
proposals. This architecture is illustrated in Figure~\ref{fig:base}.

\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/base_illustration.png}
 \caption{Base Swarm Fusion architecture.}\label{fig:base}
\end{figure}

\mysubsubsection{Relationships to existing methods} Our framework is
general, and it is easy to verify that existing parallel fusion
algorithms are just our special cases.
%
For example, the parallel fusion algorithm by Lempitsky et
al.~\cite{viktor} always performs binary fusion between the current
solution and another label, which can be achieved by setting $\alpha_i =
1$ and $\beta_i = 0$ for all the threads. The algorithm by
Veksler~\cite{olga} or Dejong et al.~\cite{dejong} hierarchically fuses
solutions starting from solution proposals. The algorithm can be
realized by setting $\alpha_i = 1, \beta_i = 0$ initially, then use
$\alpha_i = 0, \beta_i=1$  for the rest of the algorithm.

\noindent
We now illustrate the power of Swarm Fusion framework for three problems
in Computer Vision.

% Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
% configuration, the first thread $T_1$ fuses its current solution $S_1$,
% two new proposal solutions (e.g., by randomly picking two proposal
% generation schemes), and the current solutions $(S_2, S_3, S_4)$ in the
% other three threads. This is a multi-way fusion with a non-submodular
% energy in general, and message passing algorithm such as
% TRW~\cite{kolmogorov} can be used. Sequential QPBO application is
% another.

% Our model is flexible. For example, a parallel fusion move algorithm by
% Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_i$

% , and it is easy to see that 
% Existing parallel fusion techniques are special

% Our model is flexible and

### 2016-03-08 paper/introduction.tex
yasu

We have validated our ideas on three problems in Computer Vision,
stereo, optical flow, and layered depthmap estimation. \yasu{add more
once we see results.}  Our approach is extremely simple in concept, and
will instantly benefit every Computer Vision researcher or engineer, who
currently uses fusion move algorithm to solve challenging problems. We
will share our implementation of the algorithm. The rest of the paper is
organized as follows. Section~\ref{section:related_work}....

>>>>

We have validated our ideas on three problems in Computer Vision,
stereo, optical flow, and layered depthmap estimation. \yasu{add more
once we see results.}  Our approach is extremely simple in concept, and
will instantly benefit every Computer Vision researcher or engineer, who
currently uses fusion move algorithm on multi-core environments to solve
challenging problems. We will share our implementation of the
algorithm. The rest of the paper is organized as
follows. Section~\ref{section:related_work}....
